Example and Tutorial for Vim Editor (Linux)

### 2019-12-30 _other/tikz/annotate/fs_tikz_annotate.tex
annotate plan and more vim guide

>>>>

\subsection{Anote Slope, X intercept and Y intercept}

Draw a line, then point to its slope, x and y intercepts.

\begin{enumerate}
  \item Define the slope and y-intercept: $a_i, b_i$
  \item Define and calculate the x-intercept: $c_i = -\frac{a_i}{b_i}$
  \item Define the text that should appear for each element: $a_{desca}$
  \item Drawing lines pointing to $a$, $b$ or $c$ points:
  \begin{itemize}
    \item direction: $d_i \in \left\{NE, SE, SW, NW\right\}$
    \item rotation: $0 <= e_i <= 90$, which direction points to text
    \item dist one: $f_i > 0 $, straight distance from origin
    \item dist two: $g_i > 0 $, distance of line
    \item point start: $h^o_i, h^o_i$, starting point based on the four pieces of information
    \item point end: $h^d_i, h^d_i$, ending point based on the four pieces of information
  \end{itemize}
\end{enumerate}

So end up drawing using $a$, $b$ for line, $h^o$ for one point $h*d$ line small segment.

\begin{verbatim}
\end{verbatim}
\bigskip
\begin{center}
\begin{tikzpicture}
\draw[->] (-1,0) -- (6,0) node[right] {$N_m$};
\draw[->] (0,-1) -- (0,6) node[above] {$N_{m^{\prime}}$};

### 2019-12-30 nontex/install/linux/fn_vim.Rmd
annotate plan and more vim guide

Vim ships with Debian.

Additional packages to install:

```{bash}
vim
```

Also install neo-vim

```{bash}
sudo apt-get install neovim
```

## Plug-ins

Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Two steps:

1. generate ~/.vim and ~/.vimrc folders
2. curl plug.vim to ~/.vim/autoload
3. update ~/.vimrc file with ininstructions regarding which files to install.
4. open vim, type: *:PlugInstall* or *:PlugUpdate*, should start seeing updating packages.
5. type: *:scriptnames* to see loaded plugins
6. just comment out or delete plug lines for packages no longer needed.
7. how to install a particular package? See [vimawesome](https://vimawesome.com/plugin/onedark-vim)

@@

@@

@@

```{bash}
# select text with cursor, then d for delete
d
```

>>>>

Vim ships with Debian. Also install neo-vim:

```{bash}
vim
sudo apt-get install neovim
```

Just installing onedark, neovim seems to work better than vim. Vim has delete lag, and extra white space rows at the bottom of the screen that could take up very large screen segment. Neovim with onedark does not have this issue, could be due to some basic setting differences.

## Install Vim-Plug Plug-ins manager for Vim

Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Several steps:

1. generate ~/.vim and ~/.vimrc folders
2. curl plug.vim to ~/.vim/autoload
3. update ~/.vimrc file with instructions regarding which files to install.
4. open vim, type: *:PlugInstall* or *:PlugUpdate*, should start seeing updating packages.
5. type: *:scriptnames* to see loaded plugins
6. just comment out or delete plug lines for packages no longer needed.
7. how to install a particular package? See [vimawesome](https://vimawesome.com/plugin/onedark-vim)

@@

## Install Vim-Plug Plug-ins manager for Neovim

Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Very similar steps as above for Vim:

1. curl *plug.vim* to *.local/share/nvim*. Directory different than vim
2. create nvim folder under .config, vimrc contents should be in this file: *~/.config/nvim/init.vim*
3. enter nvim and *:PlugInstall*

```{bash}
# Neovim (~/.local/share/nvim/site/autoload)
curl -fLo ~/.local/share/nvim/site/autoload/plug.vim --create-dirs \
    https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim

# create vimrc file
mkdir ~/.config/nvim
nvim ~/.config/nvim/init.vim

Vimrc file with atom styling:
```
" Plugins will be downloaded under the specified directory.
call plug#begin('~/.local/share/nvim/site/plugged')

" Declare the list of plugins.
Plug 'joshdick/onedark.vim'
Plug 'vim-airline/vim-airline'

@@

# Forward one page and back one page
# ctrl+f, ctrl+b

@@

```{bash}
# select text with cursor, then d for delete
d
# delete until end of line, outside insert mode
D
```
